---
title: "EASY Start"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this contest, we will provide you with 3 collection of data ([You could download in from google drive](https://drive.google.com/drive/folders/1_WYduu1b_x2Zvil9qdPlF69a6SKkF70b?usp=sharing) ) that we have extracted from TG-GATEs for you.

You can use these three data sets for the contest. But since data/data preprocessing is extremely important in Data Science, we strongly recommend you to read [Data Preprocessing section](data_preprocessing.html) to appreciate the real situation of Big Data and Data Science in Biology and Medicine, in my point of view,  which is the most import things you should take home after the contest. 

Then let's get of a general idea of our data. we show this in R but you can use Python for this purpose too. 
Actural, we use Python for all the following analysis after we get these three data set as we can use popular machine learning([scikit-learn](http://scikit-learn.org/stable/)) and deep learning tools([Tensorflow](https://www.tensorflow.org/)) in Python. 

---


## Data description

* exprs_train.csv - This is data that you should use when you train the model

* exprs_test.csv - With this data, you make predictions and we will calculate scores for each team based on unpublished data "pathology_test.csv"

* pathology_train.csv - this is the labels corrsponding to samples in exprs_train.csv file 

## How to use these data

### Drug-response gene differential expression data

"exprs" data here are drug-response gene differential expression data of rat in vivo liver collected from TG-GATEs. For the details, please check [Data Preprocessing section](data_preprocessing.html). But if you want to get start as soon as possible, you can regard it just as a matrix whose rows are samples and columns are features 

We load exprs_train data in R and explain a bit more as you will need this knowledge in stage two and three.
```{r}
exprs_train=read.csv("../TGGATEs_tutorial_secrete/data/exprs_train.csv",header = TRUE,row.names = 1)
head(exprs_train[,1:6])
dim(exprs_train)


```

As you can see, rownames of expression data have format "durg/compound_time_dose level".
So this means this row is the gene differential expression data of liver for the  rat that was administered "drug/compound" with "dose level" and sacrificed at "time point" for measurement. From "drug/compound", you can collect more information and thus *‘making-a-bigger-box’* in **stage 3**.

And colnames of expression data are gene names. So each column is gene diffrential  expression level across all the samples. You may notice already that we have more features than samples in our data.This is general problem we will encoutnter when  applying machine learning techniques in Biology/Medicine. The aims of **stage 2** is trying to using feature selection methods to reduce the number of features but having equivelant prediction power at the same time. 

### pathology data
Pathology data are pathological records corresponding to samples in expression data. 

```{r}
pathology_train=read.csv("../TGGATEs_tutorial_secrete/data/pathology_train.csv",header = TRUE,row.names = 1)
head(pathology_train)
```
You can see we provide you with two  pathologies "Microgranuloma" and "Hypertrophy". In **stage 1** , it's up to you to  predict them sepretatly or try to predict two patholgies simultaneously (For example, by [multi-label classification](https://en.wikipedia.org/wiki/Multi-label_classification))

---



